Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-11-03 AtmoSwing - Geoscientific Model Development/template.tex
Moving GAs out of the AtmoSwing article.

The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors). It relies on the fact that similar meteorological influences are likely to result in similar local effects. This statistical relationship is thus based on archive of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.

@@

\begin{itemize}
	\setlength\itemsep{-1mm}
	\item Brier Score \citep{Brier1950, Toth2003}
	\item ROC diagramm \citep[Relative Operating Characteristic or Receiver Operating Characteristic,][]{Mason1982}
	\item RPS \citep[Ranked Probability Score,][]{Epstein1969}
	\item SEEPS \citep[Stable Equitable Error in Probability Space,][]{Rodwell2010,Rodwell2011}
\end{itemize}

@@

Due to the limitation of the sequential approach, we implemented a global optimization technique based on Genetic algorithms. This allows for a fully automatic and objective optimization of the AM. However, as this topic is rather consequent, it will be the subject of another publication.

>>>>

The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors). It relies on the fact that similar meteorological influences are likely to result in similar local effects. This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.

@@

\begin{itemize}
	\setlength\itemsep{-1mm}
	\item Brier Score \citep{Brier1950}
	\item ROC diagramm \citep[Relative Operating Characteristic or Receiver Operating Characteristic,][]{Mason1982}
	\item RPS \citep[Ranked Probability Score,][]{Epstein1969}
	\item SEEPS \citep[Stable Equitable Error in Probability Space,][]{Rodwell2010,Rodwell2011}
\end{itemize}

@@

Due to limitations of the sequential approach, we decided to explore optimization techniques that can handle all parameters fully automatically. We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose. Because of the complexity of the AM and its non-linearity, a technique of global optimization is required. We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM. This allows for a fully automatic and objective optimization of the AM. However, as this topic is rather consequent and the code base is not yet released, it will be the subject of another publication.

### 2015-11-03 Genetic algorithms - Journal of Climate/template.tex
Moving GAs out of the AtmoSwing article.

\abstract{

	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).

	These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.

	}

@@

We thus decided to explore optimization techniques that can handle all parameters fully automatically. We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose. Due to the complexity of the AM and its non-linearity, a technique of global optimization is required. We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM. This article is not about discussing the results of such a technique, but describing the details of the implementation. The demonstration of the benefit brought by such an approach is the topic of another article. The details of the implementation being numerous, the description is provided in the next dedicated section (\ref{sec:gas}).

>>>>

\abstract{The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
	These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
	}

@@

 This article is not about discussing the results of such a technique, but describing the details of the implementation. The demonstration of the benefit brought by such an approach is the topic of another article.
